(Working Title) Stellar and Planetary Properties of \KT\ \Ci\ Candidates and Confirmation of $N$ Systems, (Including a Planet Receiving Earth-like Insolation?)

### 2015-03-05 ms.tex
Revert "sorry bogus merge conflicts because of bogus hard wrap"
This reverts commit 69d7b2de27ba703d4c284e06966c3a21b757ce23, reversing
changes made to b16f301aa6d5b40adb30b7988176c89e0b8ee798.

\KT\ light curves produced with aperture photometry contain substantial pointing-induced
photometric variations caused by the star's apparent motion over a poorly-defined flat
field.
Worse yet, these variations occur on timescales similar to transit signals, potentially
masking the observational signature of a planet passing between \kep\ and the host 
star.

@@

\paperit{} simultaneously fit both the systematics and potential planetary transit signals
in a search for transiting planets.
The authors of that paper assume that the dominant trends in the observed stellar light
curves are caused by spacecraft motion and are shared among many stars. \anytodo{Among,
right? Not between?}
They then run PCA on all stars to measure the dominant modes, modeling each star as a

linear combination of 150 of these ``eigen light curves'' and a transit signal.
This method enables fitting without over-fitting, and also permits marginalization 
over
uncertainties induced by the noise model.
Therefore, any uncertainties in the systematics can be propogated into uncertainties 
in
detected planet parameters, instead of assuming the systematics are understood 
perfectly.
Using this technique, \paperit{} detect 36 planet candidates orbiting 31 stars in \KT\
\Ci\ data.

@@

In this paper, we present stellar and planetary parameters for each system.

Given these parameters and the transit data, as well as archival imaging, ground-based
seeing limited survey data, and adaptive optics imaging, we are able to confirm
\anytodo{Number} of these systems as transiting planets at the \anytodo{Sigma} confidence
level. We also are able to confirm \anytodo{Number} of these systems as false positives.

@@

Such a scheme enables us to infer the statistical uncertainties on the
mass, radius, and effective temperature.

However, we are subject to biases induced by systematics in the models themselves.
There is some evidence that the Dartmouth models may underpredict
radii by $\sim 15\%$ when compared to other methods \citep{Newton15,
Montet15}.
Such an effect may be the result of the Dartmouth model reliance on BT-Settl
atmospheres, which have been shown to predict near-IR colors that are too blue
\citep{Thompson14}.
We find that by measuring stellar parameters without any WISE data (that is, using
only $BVgriJHK$), we largely reproduce the same effective temperatures as when
the WISE data is included.
However, at the low-mass end including the WISE data systematically increases the
measured radius and increases \logg, as shown in \btmtodo{Figure}.
Suggestively, spectroscopic stellar parameters of EPIC 201912552
(\textsection\ref{Spexobs}) suggest the derived photometric properties better
represent the true physical parameters when the WISE data is included.

@@

\teff\ was calculated by comparing our optical spectra with the CFIST
suite\footnote{http://phoenix.ens-lyon.fr/Grids/BT-Settl/CIFIST2011/} of the BT-SETTL
version of the PHOENIX atmosphere models \citep{Allard13}, which gave a temperature
of 3503 $\pm$ 60\,K.
More details of this procedure are given in \citet{Mann14} and
\citet{Gaidos14}.
This method was used because it is known to accurately reproduce empirical
\teff\ values from long-baseline optical interferometry \citet{Boyajian12}.

@@

\subsection{Multiple Planet Systems}
Five of the systems identified by \paperit\ are candidates to be multiply-transiting
systems.
One of these is EPIC 201367065, a three-planet system originally announced by

\citet{Crossfield15}.
Another of these is EPIC 201505350 \citep{Armstrong15b}, a two-planet system with the
orbital periods of the two planets near a 3:2 period commensurability.
The remaining three are all representative of the multiple-planet systems observed 
by
\kep \citep{Lissauer11b, Fabrycky14}.
Two of the systems are near a period commensurability and all three consist of
mini-Neptune sized planets.
Like in the \kep\ field, the false positive rate we measure for the multiple planet 
sample
here ($0/10$) is lower than for the single systems \citep{Lissauer12, Rowe14}.

We do not detect any significant transit timing variations (TTVs) in any of these systems from
the \KT\ data alone.
EPIC 201338508 would be expected to have a TTV period of 117 days, but
is likely too far from commensurability to have an observable TTV signal.
EPIC 201445392 is expected to have a TTV period of 234 days, so this system may be a candidate
for additional follow-up to constrain the system masses dynamically.
The transiting planets orbiting EPIC 201754305 are near a 5:2 period commensurability.
There is no evidence from \kep\ of an abundance of planets near this period ratio, and so this
may be coincidence.
Follow-up observations may be warranted to search for an additional planet in this system
forming a resonant chain, similar to those observed around other stars \citep[e.g.][]{Swift13,
Campante15}.

@@

\include{table_planets}

>>>>

\KT\ light curves produced with aperture photometry contain substantial pointing-
induced
photometric variations caused by the star's apparent motion over a poorly-defined 
flat 
field. 
Worse yet, these variations occur on timescales similar to transit signals, potentially
masking the observational signature of a planet passing between \kep\ and the host 
star.

@@

\paperit{} simultaneously fit both the systematics and potential planetary transit 
signals
in a search for transiting planets. 
The authors of that paper assume that the dominant trends in the observed stellar 
light
curves are caused by spacecraft motion and are shared among many stars. 
\anytodo{Among,
right? Not between?}
They then run PCA on all stars to measure the dominant modes, modeling each 
star as a 
linear combination of 150 of these ``eigen light curves'' and a transit signal.
This method enables fitting without over-fitting, and also permits marginalization 
over
uncertainties induced by the noise model.
Therefore, any uncertainties in the systematics can be propogated into uncertainties 
in
detected planet parameters, instead of assuming the systematics are understood 
perfectly.
Using this technique, \paperit{} detect 36 planet candidates orbiting 31 stars in \KT\
\Ci\ data.

@@

In this paper, we present stellar and planetary parameters for each system.
Given these parameters and the transit data, as well as archival imaging, ground-
based
seeing limited survey data, and adaptive optics imaging, we are able to confirm 
\anytodo{Number} of these systems as transiting planets at the \anytodo{Sigma} 
confidence
level. We also are able to confirm \anytodo{Number} of these systems as false 
positives.

@@

Such a scheme enables us to infer the statistical uncertainties on the
mass, radius, and effective temperature.
However, we are subject to biases induced by systematics in the models 
themselves.
There is some evidence that the Dartmouth models may underpredict 
radii by $\sim 15\%$ when compared to other methods \citep{Newton15,
Montet15}. 
Such an effect may be the result of the Dartmouth model reliance on BT-Settl
atmospheres, which have been shown to predict near-IR colors that are too blue
\citep{Thompson14}.
We find that by measuring stellar parameters without any WISE data (that is, using
only $BVgriJHK$), we largely reproduce the same effective temperatures as when
the WISE data is included. 
However, at the low-mass end including the WISE data systematically increases the 
measured radius and increases \logg, as shown in \btmtodo{Figure}.
Suggestively, spectroscopic stellar parameters of EPIC 201912552 
(\textsection\ref{Spexobs}) suggest the derived photometric properties better 
represent the true physical parameters when the WISE data is included.

@@

\teff\ was calculated by comparing our optical spectra with the CFIST
suite\footnote{http://phoenix.ens-lyon.fr/Grids/BT-Settl/CIFIST2011/} of the BT-
SETTL
version of the PHOENIX atmosphere models \citep{Allard13}, which gave a 
temperature
of 3503 $\pm$ 60\,K. 
More details of this procedure are given in \citet{Mann14} and
\citet{Gaidos14}. 
This method was used because it is known to accurately reproduce empirical 
\teff\ values from long-baseline optical interferometry \citet{Boyajian12}.

@@

\subsection{Multiple Planet Systems}
Five of the systems identified by \paperit\ are candidates to be multiply-transiting
systems. 
One of these is EPIC 201367065, a three-planet system originally announced by
\citet{Crossfield15}. 
Another of these is EPIC 201505350 \citep{Armstrong15b}, a two-planet system 
with the
orbital periods of the two planets near a 3:2 period commensurability.
The remaining three are all representative of the multiple-planet systems observed 
by
\kep \citep{Lissauer11b, Fabrycky14}.
Two of the systems are near a period commensurability and all three consist of 
mini-Neptune sized planets.
Like in the \kep\ field, the false positive rate we measure for the multiple planet 
sample
here ($0/10$) is lower than for the single systems \citep{Lissauer12, Rowe14}.

We do not detect any significant transit timing variations (TTVs) in any of these 
systems from 
the \KT\ data alone. 
EPIC 201338508 would be expected to have a TTV period of 117 days, but 
is likely too far from commensurability to have an observable TTV signal. 
EPIC 201445392 is expected to have a TTV period of 234 days, so this system may 
be a candidate
for additional follow-up to constrain the system masses dynamically. 
The transiting planets orbiting EPIC 201754305 are near a 5:2 period 
commensurability. 
There is no evidence from \kep\ of an abundance of planets near this period ratio, 
and so this 
may be coincidence.
Follow-up observations may be warranted to search for an additional planet in this 
system 
forming a resonant chain, similar to those observed around other stars \citep[e.g.][]
{Swift13,
Campante15}.

@@
